\documentclass{sig-alternate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LATEX DEFINITIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{hyperref}
\usepackage{array}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{pifont}
\usepackage{todonotes}
\usepackage{rotating}
\usepackage{color}

\newcommand*\rot{\rotatebox{90}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
\CopyrightYear{2014} 
\crdata{X-XXXXX-XX-X/XX/XX}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Sicientific Impact Metrics for XSEDE%
\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\texttt{www.acm.org/eaddress.htm}}}

\numberofauthors{4} 
\author{
\alignauthor
Gregor von Laszewski\titlenote{Corresponding Author.}\\
       \affaddr{Indiana University}\\
       \affaddr{2719 10th Street}\\
       \affaddr{Bloomington, Indiana, U.S.A.}\\
       \email{laszewski@gmail.com}
% 2nd. author
\alignauthor
Fugang Wang\\
       \affaddr{Indiana University}\\
       \affaddr{2719 10th Street}\\
       \affaddr{Bloomington, Indiana, U.S.A.}\\
% 3rd. author
\alignauthor
Geoffrey C. Fox\\
       \affaddr{Indiana University}\\
       \affaddr{2719 10th Street}\\
       \affaddr{Bloomington, Indiana, U.S.A.}\\
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor 
Tom Furlani\\
       \affaddr{CRC}\\
       \affaddr{Street}\\
       \affaddr{Buffalo NY, 47401}
}
\date{13 March 2014}


% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{h-index, metric, FutureGrid, Technology audit, XSEDE}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TOC
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LIST OF TODOS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\listoftodos

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TITLE OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{arabic}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{abstract}

TBD

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{introduction}

\input{requirements}

\input{design}

\input{implementation}

\input{related}

\input{evaluation}

\input{conclusion}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section*{Acknowledgement}

TAS Grant ... \todo{tas grant}

Some of the text published in this chapter is available form the
FutureGrid portal. The FutureGrid project is funded by the National
Science Foundation (NSF) and is led by Indiana University with
University of Chicago, University of Florida, San Diego Supercomputing
Center, Texas Advanced Computing Center, University of Virginia,
University of Tennessee, University of Southern California, Dresden,
Purdue University, and Grid 5000 as partner sites. This material is
based upon work supported in part by the National Science Foundation
under Grant No. 0910812. If you use FutureGrid and produce a paper or
presentation, we ask you to include the reference
\cite{las2010gce,las12fg-bookchapter}.

\bibliographystyle{IEEEtranS}
\bibliography{%
bib/references,%
bib/vonLaszewski-jabref,%
bib/image-refs,%
bib/cyberaide-cloud,%
bib/python}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage

%\appendix

\end{document}
